\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Assessing economic inequality with tax data - Switzerland from 1945 to 2010}

### 2014-06-17 paper/subdocuments/results.Rnw
applied relative distribution methods to compare FTA and HBS data

@@

%ABBILDUNGEN ZUM VERGLEICH NORMAL-/SONDERFÄLLE
<<specialcases9394, echo=FALSE,warning=FALSE>>=
library(dplyr, quietly=TRUE, warn.conflicts = FALSE)
library(ggplot2)
#library(reldist)
normal <- read.csv("../../data/ginis_und_perzentile_normal.csv",sep="\t")
normal <- normal %.% select(-G_reink, -G_taxed, -ppop0, -G_steink0)
pooled <- read.csv("../../data/ginis_und_perzentile_beides.csv",sep="\t")
#special <- read.csv("data/ginis_und_perzentile_sonder.csv",sep="\t")
normal$case <- "normal case"
#special$case <- "special case"
pooled$case <- "pooled, normal and special cases"
d<-rbind(normal,pooled)
d<-d %.% 
  filter(kanton=="CH",steuerperiode==1993.5)

@@

#plot relative distribution
rel <- data.frame(pooled$inc,normal$inc,pooled$percentile)
rel$change <- rel$pooled.inc/rel$normal.inc
ggplot(rel, aes(x=pooled.percentile,y=change))+
	geom_line()+theme_bw()+
	scale_colour_grey()+
	geom_line(linetype="dashed",aes(y=1),size=2)+
	xlab("Percentile")+ylab("taxable income")+
	ggtitle("Taxable incomes of normal versus special cases 1993/94")

@@

\emph{normal and special cases}

>>>>

% Nicht eher nur CH-Plot?

@@

%ABBILDUNGEN ZUM VERGLEICH NORMAL-/SONDERFÄLLE
<<specialcases9394, echo=FALSE,warning=FALSE>>=
library(dplyr, quietly=TRUE, warn.conflicts = FALSE)
library(ggplot2)
#library(reldist)
normal <- read.csv("../../data/ginis_und_perzentile_normal.csv",sep="\t")
normal <- normal %.% select(-G_reink, -G_taxed, -ppop0, -G_steink0)
pooled <- read.csv("../../data/ginis_und_perzentile_beides.csv",sep="\t")
#special <- read.csv("data/ginis_und_perzentile_sonder.csv",segep="\t")
normal$case <- "normal case"
#special$case <- "special case"
pooled$case <- "pooled, normal and special cases"
d<-rbind(normal,pooled)
d<-d %.% 
  filter(kanton=="CH",steuerperiode==1993.5)

@@

#plot relative distribution
rel <- data.frame(pooled$inc,normal$inc,pooled$percentile)
rel$change <- rel$pooled.inc/rel$normal.inc
ggplot(rel, aes(x=pooled.percentile,y=change))+
	geom_line()+theme_bw()+
	scale_colour_grey()+
	geom_line(linetype="dashed",aes(y=1),size=1)+
	xlab("Percentile")+ylab("taxable income")+
	ggtitle("Taxable incomes of normal versus special cases 1993/94")

@@
